### 2016-06-23 sec5_spm-bk.tex
Lets fix sec 6!!
aaaaa

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension 
and results in groups of snapshots in each partition. 
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
are mined GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

It is challenging to directly find the optimal $\Gamma$. 
First, suppose there are $n!$ permutation matrices. 
Such a high complexity is trivially unpractical. Second,
since $G$ is unknown in prior,
the vertex order cannot be planned beforehand. 
Despite these challenges, we find a simple $O(1)$ time 
solution which is good enough as stated in the 
following theorem.

\begin{theorem}[Balance of Star Partition]
\label{THM:SPM_LB}
Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
Let $\Gamma^*$ be optimal size of straggler among all vertex orders.
Let $\Gamma$ be the size of straggler wrt an random vertex order $P$. 
With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
That is,  with probability $1-1/n$, 
$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}

In fact, we have a tighter bound of $(\Gamma - \Gamma^*)$ if 
the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
Utilizing Theorem~\label{THM:SPM_LB}, in star partition, it is safe 
to choose the object IDs as the vertex order. This because real object IDs are often 
hashed and can be deemed as random.

@@

\begin{example}
In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
Let $L=2,K=3,G=2$, then both candidates are not valid patterns. 
However, the timestamps of their super set $\{o_1,o_2,o_3\}$ is $P_1.T \cap P_2.T=\{1,2,3\}$, which
conform to $L,K,G$. This indicates that even though $P_1.O$ and $P_2.O$ are not valid patterns, they
cannot be pruned. Otherwise, $\{o_1,o_2,o_3\}$ would be missed out.
\end{example}

\subsubsection{Monotonicity}
To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists. For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$. To generalize the idea, we propose two concepts named \textit{maximal $G$-connected subsequence} and \emph{candidate sequence}.

@@

\begin{example}
Let $G=2$, consider $T_1=(1,2,4,5,6,9,10,11,13)$. $T_1$ has two maximal $2$-connected subsequences:
$T_1^A=\{1,2,4,5,6\}$ and $T_1^B=\{9,10,11,13\}$. Consider $T_2=(1,2,4,5,6,8,9)$,
since $T_2$ is $2$-connected, thus $T_2$ has only one maximal $2$-connected subsequence which is
itself.
%Let $G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$
%%
% XXX EXPLAIN HOW TO DERIVE THE MAXIMAL G-CONNECTED SUBSEQUENCES OF $T_1$ and $T_2$. 
\end{example}

\begin{definition}[Candidate Sequence]
$T$ is a candidate sequence if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
\end{definition}

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a candidate sequence
since one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a candidate sequence because it has one maximal $2$-connected subsequence
and it is $2$-consecutive with size greater than $4$.
\end{example}

@@

\begin{definition}[Sequence Simplification]
Given a sequence $T$ and the GCMP parameters $G,L,K$, a $T^\#$ is
the simplified sequence of $T$ if (1) $T^\#$ is contained in $T$, i.e., $T^\# \subseteq T$.
(2) $T^\#$ is a candidate sequence, and (3) no other candidate sequence
$T^\#_1$ is contained in $T$ and contains $T^\#$.
%GIVEN A SEQUENCE, PLEASE UNIQUELY DEFINE ITS SIMPLIFICATION OUTPUT.
\end{definition}
Note that, not every $T$ has the simplified sequence.  For example, if $L =3$,
then the simplified sequence of $(1,2,5,6)$ does not exists.
Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
as stated in the following theorem:
\begin{theorem}
For any sequence $T$, if $T$'s simplified sequence is not empty, then
there exists a unique $T^\#$ wrt $T$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$. We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction. For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.

Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$. Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
there are four cases to be considered. 
We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
\begin{figure}[h]
\centering
\includegraphics[width=0.46\textwidth]{thm3proof.eps}
\caption{Proof of theorem 3 with the four cases.}
\label{fig:proof_thm_3}
\end{figure}
\begin{itemize}
\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$. Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$. Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
\item Case (c): $c-f > G$ and $e-h \leq G$. In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.  Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
\item Case (d): $c-f > G$ and $ e- h > G$. In this case,  $\overline{ef}$ has to be a candidate sequence. Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
\end{itemize}
In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
\end{proof}

Next, we design an efficient simplification process with linear complexity.
It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.

\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---$L$ Phase---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] > 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---$G$-$K$ Phase---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{example}
Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
\end{example}

With the concepts of \textit{candidate sequence} and \textit{sequence simplification}, we are ready to define the monotonic property that can be used for pruning.
\begin{theorem}\label{THM:SPM_TM}
Given a candidate pattern $P=\{O:T\}$, if sequence $P.T$ cannot be simplified to a candidate sequence, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

\begin{proof}
Let $P_2$ be a true pattern with $P_2.O \supseteq P.O$. It is easy to see that $P_2.T \subseteq P.T$. Since $P_2.T$ conforms to $G,L,K$. This indicates that $P_2.T$ is indeed a candidate sequence. Since $P_2.T \subseteq P.T$, $P.T$ can be simplified to candidate sequence (i.e., to $P_2.T$) which contradict with the fact that $P$ cannot be simplified. Thus no such true pattern exists.
\end{proof}

@@

\subsubsection{Apriori Algorithm}

To systematically discover valid patterns in each star, 
we design the \emph{Apriori Mining} algorithm. 
To describe the  algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State{Simply $e(s,t)$} \Comment{ Simplification}
\State {Ground.add($\langle \{s,t\}, T \rangle$)}
\State {Lv $\gets$ Ground}
\EndFor
\While{Lv is not empty}
		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
		\State {Remove false patterns in Lv}
		\Comment{Monotonicity}
		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
			\State{output.add(Lv)} 
			\State{break}
		\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}

An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
higher level candidates are generated by joining lower level candidates. When no more candidates 
can be generated, the algorithm stops by outputting the valid patterns.
%
%It is notable that, in star partition, original data is 
%replicated at most $O(|\mathbb{O}|)$ times.
%In later sections, we will describe several 
%more optimization techniques to further reduce the amount of replicated data.

>>>>

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant work.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

Although it is very challenging to find the optimal vertex id ordering from the $n!$ possibilities, we observe that a random order can actually achieve satisfactory performance based on the following theorem.

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
In Appendix XXX.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
In Appendix XXXX.
\end{proof}
Hence, we can simply use object id to determine the vertex ordering in our implementation.

@@

\begin{example}
In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
Let $L=2,K=3$ and $G=2$. Both candidates are not valid patterns because the constraint on $L$ is not satisfied. 
However, when considering their object superset $\{o_1,o_2,o_3\}$, we can infer that their co-clustering timestamps are in $(1,2,3)$. This is a valid pattern conforming to the constraints of $L,K,G$. Thus, we need a new type of monotonicity to facilitate pruning.
\end{example}

\subsubsection{Monotonicity}
To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists. For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$. To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.

@@

\begin{example}
Suppose $G=2$ and consider two sequences $T_1=(1,2,4,5,6,9,10,11,13)$ and $T_2=(1,2,4,5,6,8,9)$. $T_1$ has two maximal $2$-connected subsequences:$T_1^A=(1,2,4,5,6)$ and $T_1^B=(9,10,11,13)$. This is because the gap between $T_1^A$ and $T_1^B$ is $3$ and it is impossible for the timestamps from  $T_1^A$ and $T_1^B$ to form a new subsequence with $G\leq 2$. Since $T_2$ is $2$-connected, $T_2$ has only one maximal $2$-connected subsequence which is
itself. 
\end{example}

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$. Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$. Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$. If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected. If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$. Both cases lead to contradiction.
\end{proof}

\begin{lemma}\label{lemma:subset-property}
If $T_1$ is a subset of $T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that $T_1'$ is a subset of $T_2'$.
\end{lemma}
\begin{proof}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

\begin{definition}[Decomposable Sequence]
$T$ is decomposable if for any of its maximal $G$-connected subsequence $T'$, we have (1) $T'$ is $L$-consecutive; and (2) $|T'|\geq K$.
\end{definition}

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than than $4$.
\end{example}

@@

\begin{definition}[Sequence Simplification]
Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
\begin{enumerate}
\item $f$-step: remove segments of $T$ that are not $L$-consecutive;
\item $g$-step: among the maximal $G$-connected subsequences of $f_L(T)$, remove those with size smaller than $K$.
\end{enumerate}
\end{definition}

\begin{example}
Take $T=(1,2,4,5,6,9,10,11,13)$ as an example for sequence simplification. 
Let $L = 2, K = 4$ and $G = 2$. In the $f$-step, $T$ is reduced to $f_2(T)=(1,2,4,5,6,9,10,11)$. 
The segment $(13)$ is removed due to the constraint of $L=2$. 
$f_2(T)$ has two maximal $2$-consecutive subsequences: $(1,2,4,5,6)$ and $(9,10,11)$. 
Since $K=4$, we will remove $(9,10,11)$ in the $g$-step. Finally, the output is $\mathtt{sim}(T)=(1,2,4,5,6)$.
\end{example}

It is possible that the simplified sequence $\mathtt{sim}(T)=\emptyset$. For example, Let $T=(1,2,5,6)$ 
and $L=3$. All the segments will be removed in the $f$-step and the output is $\emptyset$.
We define $\emptyset$ to be not decomposable. 
%Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
We provide an important property of the sequence simplification process as follows:
\begin{lemma}\label{lemma:decom-sim}
If sequence $T$ is a superset of any decomposable sequence, then $\mathtt{sim}(T) \neq \emptyset$.
\end{lemma}
\begin{proof}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

Suppose $T_p$ can be decomposed into a set of maximal $G$-connected
subsequences $T_p^1, \ldots, T_p^m$ ($m \geq 1$). Since $T_p$ is a subset of $T$, all the $T_p^i$ are also subsets of $T$. By definition, each $T_p^i$ is $L$-consecutive. Thus, in the $f$-step of $\mathtt{sim}(T)$, none of $T_p^i$ will be removed. In the $g$-step, based on Lemma~\ref{lemma:subset-property}, we know that each $T_p^i$ has a superset in the maximal $G$-connected subsequences of $f_L(T)$. Since $|T_p^i|\geq K$, none of $T_p^i$ will be removed in the $g$-step. Therefore, all the $T_p^i$ will be retained after the simplification process and $\mathtt{sim}(T) \neq \emptyset$.
\end{proof}

\eat{
Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
as stated in the following theorem:
\begin{theorem}
For any sequence $T$, if $T$'s simplified sequence is not empty, then
there exists a unique $T^\#$ wrt $T$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$. We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction. For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.

Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$. Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
there are four cases to be considered. 
We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
\begin{figure}[h]
\centering
\includegraphics[width=0.46\textwidth]{thm3proof.eps}
\caption{Proof of theorem 3 with the four cases.}
\label{fig:proof_thm_3}
\end{figure}
\begin{itemize}
\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$. Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$. Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
\item Case (c): $c-f > G$ and $e-h \leq G$. In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.  Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
\item Case (d): $c-f > G$ and $ e- h > G$. In this case,  $\overline{ef}$ has to be a candidate sequence. Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
\end{itemize}
In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
\end{proof}
}

\eat{
Next, we design an efficient simplification process with linear complexity.
It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.

\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---$L$ Phase---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] > 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---$G$-$K$ Phase---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}
}

With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
sequences to facilitate the pruning in the Apriori algorithm.

\begin{theorem}[Monotonicity]\label{THM:SPARE_MONO}
Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

\begin{proof}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on the Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

\subsubsection{Apriori Enumeration}
We then design the Apriori enumeration method to
systematically discover all valid patterns in a star.
%During the enumeration, we refer a candidate pattern
%$P$ as a $R$-candidate if $|P.O|=R$.
The enumeration method discover patterns iteratively using ``bottom-up'' order:
candidates with smaller objects set grow one object per iteration.
%
%in iteration $i$,  all $(i+1)$-candidates grows
%to $(i+2)$-candidates.
%
Enumeration ends if no
further candidates can be generated.

 Due the \emph{monotonicity} proved in Theorem~\ref{THM:SPARE_MONO}, we are able to use the \emph{monotonic pruning} and \emph{forward closure check} to boost the enumeration process. We show the detail of the process
in Algorithm~\ref{algo:apriori_mining}. As a start, 
each input edge is treated as a candidate pattern, with the 
inverted list as the time sequence. These candidates
are kept in $\mathbf{G}$ as the ground set (Lines~\ref{code:init-start}-\ref{code:init-end}). In initialization, the inverted lists are simplified (Line~\ref{code:simp1}) and unqualified lists are pruned (Line~\ref{code:init-prune}). Throughout the algorithm, we maintain a set of candidates $\mathbf{C}$ which is initialized to the ground set $\mathbf{G}$ (Line~\ref{code:init-C}).

In each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}),  the members in candidate set are joined with the members in ground set to generate new candidates (Lines~\ref{code:join-start}-\ref{code:join-ends}). The join of two candidates $c$ and $g$ creates a 
new candidate, whose objects are the union of $c.O$ and$g.O$ and the time sequence is the intersection of $c.T$ and $g.T$ (Line~\ref{code:join}). During the join,
we use \emph{sequence simplification} to detect unqualified candidates. By \emph{monotonicity}, these candidates are safely excluded from the future iterations~(Line~\ref{code:mono-pruning}). If a valid candidate is not able to be extended by any ground set, we directly output it (Line~\ref{code:output1}).

After the join finishes, we start a \emph{forward closure} check (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-ends}). We test whether the union of all candidates in $\mathbf{C}$ forms a valid pattern. If the check succeeds, we output such union and stop the iteration~(Lines~\ref{code:fc-checking}).

\eat{
to union all the candidates in the current candidate set, and quickly check whether the

To systematically discover valid patterns in each star,

we enumerate all valid patterns in ``bottom-up" order: 
pattern candidates with smallest object sizes are enumerated
first and grew to pattern candidates with larger object sizes.
During the enumeration, we call a candidate pattern
$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
a star as input, and treat each edge as a $2$-pattern.

The input of
the enumerator is a star. Each edge
in the star is treated a $2$-candidate, with the inverted
list to be the time sequence.

we design the \emph{Apriori Mining} algorithm. We borrow
the terminologies in classic Aprirori algorithm: a candidate
pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
candidates grows from $2$-pattern level by level.

To describe the algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
}

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$} \label{code:init-start}
\State {$T' \gets \mathtt{sim}(e(s,t))$} \label{code:simp1}
\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}\label{code:init-prune}
\EndFor\label{code:init-end}
\State {$\mathbf{C} \gets \mathbf{G}$}\label{code:init-C}
\While{$\mathbf{C} \neq \emptyset$} \label{code:level-start}
		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
		\ForAll{$(c,g)\in \mathbf{C}$} \label{code:join-start}
			\ForAll {$g \in \mathbf{G}$}		
				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$} \label{code:join}
				\State {$\mathbf{N}$.add$(c')$, unless $c'.T \neq \emptyset$} \label{code:mono-pruning}
			\EndFor
			\State $\mathbf{OT}$.add$(c)$, if $c$ is not extended.\label{code:output1}
		\EndFor	\label{code:join-ends}
		\State {$\mathbf{C} \gets \mathbf{N}$}
		\State $U \gets $ union of $n_i \in \mathbf{C}$	\label{code:fc-checking-start}
		\If {$U$ is a valid pattern}
			\State $\mathbf{Output}.\mathbf{add}(U)$ \label{code:fc-checking}
			\State break;
		\EndIf \label{code:fc-checking-ends}
\EndWhile\label{code:level-ends}
\State $\mathbf{OT}$.addAll$(\mathbf{C})$
\State \Return $\mathbf{OT}$
\end{algorithmic}
\end{algorithm}

%An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
%As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
%higher level candidates are generated by joining lower level candidates. When no more candidates 
%can be generated, the algorithm stops by outputting the valid patterns.
%
